Using the {\tt MovingRegionAlgebra}

### 2006-02-23 Algebras/MovingRegion/Intro/Intro.tex
Fixed some typos.

During development and initial tests with the \mra, it has been noticed
that there is not much suitable data available which can be used to build
\mr\ objects. As a workaround, Thomas Behr of the Feruniversit"at Hagen
has created the
{\tt Region2MRegion} converter, which applies a list of affine
transformations to a {\tt region} object to construct a \mr\ object.

@@

\bibitem[GuS04]{GuS04}
  R.\ H.\ G"uting, M.\ Schneider.
  \textsl{Moving Objects Databases}.
  Vorlesung an der Fernuniversit"at Hagen, 2004.

>>>>

During development and initial tests with the \mra, it has been noticed
that there is not much suitable data available which can be used to build
\mr\ objects. As a workaround, Thomas Behr of the Feruniversit\"{a}t Hagen
has created the
{\tt Region2MRegion} converter, which applies a list of affine
transformations to a {\tt region} object to construct a \mr\ object.

@@

\bibitem[GuS04]{GuS04}
  R.\ H.\ G\"{u}ting, M.\ Schneider.
  \textsl{Moving Objects Databases}.
  Vorlesung an der Fernuniversit\"{a}t Hagen, 2004.
